Supplementary Material for ``Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)"

### 2024-02-14 ba_resubmit_template_files/response_to_reviewers4.tex

\documentclass[letterpaper, parskip]{scrartcl}

\usepackage{amsmath,amssymb,bm}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1.4in]{geometry}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage{tcolorbox}            % provides shaded box for reviewer comments
\usepackage{enumitem}             % use more compact lists
%\usepackage[parfill]{parskip}     % use skips between paragraphs and no indents
\usepackage{bibentry}             % provides \nobibliography command
\usepackage{xspace}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
	pdftitle={Overleaf Example},
	pdfpagemode=FullScreen,
}

\urlstyle{same}

@@

\begin{document}

	% ****************** TITLE ****************************************

	\title{Response to Reviewer Comments}
	\maketitle

We thank the Editor and Associate Editor for the continued valuable feedback.

@@

\section{Editor Comments}

%\pointRaised{E}{I received a detailed and careful report from the original associate editor who thinks the paper is now easier to read and understand. I still find it intricate to read, but the AE may have a point when saying that the notation can be a difficult challenge in this area of research.}
%\reply{}

\pointRaised{E}{Anyhow, I have decided to follow the AE’s recommendation and would like the authors to carefully consider the comments in the AE report and make the suggested revisions. I find the issue raised by the AE regarding the formulas in Section 4.2 particularly concerning for two reasons. First, the article cannot be accepted if it contains technical errors and inaccuracies. Second, the formulas in question were used to code up the samplers used in the simulations and data analysis examples. If the formulas are incorrect (do not make sense, in fact, as the AE points out) how can the computational results be trusted? This is a grave concern that must be satisfactorily and convincingly addressed before the manuscript is accepted for publication.}

\reply{We assure the Editor that the correct formulas we used in all samplers in the previous submission and match those suggested by the Associate Editor. This is evident in our code, which we have made available at \url{github.com/briankundinger/fabl.BA}. Simply, our notation in the previous version was imprecise. We have now corrected the notation using the Associate Editor's suggestion.}

@@

\section{Associate Editor Comments}

\pointRaised{AE}{For Section 4.2, my question starts with the definition of $\Gamma_{Z_{j^{(s+1)}, j}}.$ Is this quantity always defined for possible values of $Z$? That is, if $Z_{j}^{(s+1)} = n_A + j$, what is the meaning of $\Gamma_{n_A+j, j}$?}

\reply{The Associate Editor is correct that $\Gamma_{n_A+j, j}$ is not defined under this notation. We had attempted to remove all instances in which this notation might be implied, but we did not catch them all. We thank the AE for their thoughtful suggestions in this regard.
}

@@

\pointRaised{AE}{This notation first arises in the definition of $n_p(Z)$, which I think could easily be changed to something along the lines of $n_p(Z) = \sum_{j:Z_j \leq n_A} I(\gamma_{Z_j, j} = h_p)$.
}

\reply{Thank you for this suggestion. We have adopted this change.
}

\pointRaised{AE}{My bigger concern comes for equation (18), where I am not entirely sure what probability is being computed, or how this sampling procedure combined with equation (19) would result in a “non-match” where $Z_j = n_A + j$. I believe that the idea is to partition the possible values of $Z_j:\left( \{r_{p_j}\}, n_A + j\right)$. Then, in equation (18), the left hand side is intended to be the probability that Z falls into each part of the partition. But, in the revision, I didn’t see where the last “non-match” part of the partition is defined, and so there is no real way to select the non-match from equation (19).
}

\reply{The AE's understanding of the sampler is correct. The AE also correctly identified in the way we wrote equation (19), such that there was no real way to select the non-match option. We thank the AE for the recommended change in notation, and have adopted the recommendation. The sampling equations are now provided as follows:

@@

Define $r$ as an arbitrary set of records. We have
\begin{align}
	\label{eqn:gibbs1}
	p\left( Z_j^{(s+1)} \in r \mid \tilde{\gamma}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}N_{p_j}}{n_A}  w_{p}^{(s+1)},  & r = r_{p_j}; \\
		1- \pi^{(s+1)} , &  r = \{n_A + j\}. \\
	\end{cases}
\end{align}
Since all records in $A$ sharing the same agreement pattern with $B_j$ are equally likely, we then sample among candidate records uniformly using
\begin{align}
	\label{eqn:gibbs2}
	p\left(Z_j^{(s+1)} = q \mid Z_j^{(s+1)} \in r, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)} \right) = \begin{cases} 
		\frac{1}{N_{p_j}}, & r = r_{p_j} \text{ and } q \in r; \\
		1, & r = \{n_A + j\} \text{ and} \\
		& q = n_A + j. \\
	\end{cases}
\end{align} 
}

\pointRaised{AE}{Also, it’s not clear to me as currently written that the authors are equating the patterns with that partition so that by definition a “true” match that does not appear in A cannot have a pattern that appears in $\mathcal{P}$, but did not happen to be observed (because the match was not captured in $A$).
}

\reply{We believe that the revised notation addresses this concern.
}

### 2024-02-14 ba_resubmit_template_files/main4.tex
new stuff

In this article, we propose fast beta linkage (\texttt{fabl}), which extends the \texttt{BRL} model for increased efficiency and scalability. We use independent prior distributions for the matching statuses of each record, and modify the decision theoretic technique of \cite{sadinle_bayesian_2017} to ensure our linkage estimates are bipartite. This approach allows us to (1) employ hashing techniques that speed up calculations and reduce computational costs, (2) compute the pairwise record comparisons over large data files via parallel computing, and (3) reduce memory costs through what we call storage efficient indexing. These contributions allow \texttt{fabl} to perform record linkage on much larger data files than previous Bayesian Fellegi-Sunter models at significantly increased speed with similar levels of accuracy. In particular, computation time under \texttt{BRL} grows quadratically, with the size of each data file, while computation time under \texttt{fabl} grows linearly, only with the size of the smaller data file.

@@

In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data.

@@

@@

Similarly, the posterior updates for $\bm{Z}$ depend on the data only through quantities calculated through $\mathcal{N}, \mathcal{P}$, and $\mathcal{R}$. For each pattern $p$, let $w_p =m_p/u_p$.  The contribution to the likelihood in the full conditional for $Z_j$ can be expressed as
\begin{align}
	\mathcal{L}(Z_j\mid  \tilde{\gamma}, \bm{m}, \bm{u}, \pi) = \prod_{p=1}^P u_p^{N_{p_j}} \prod_{i \in r_{p_j}} w_p^{I(Z_j = i)}. \label{likelihood_efficient_z}
\end{align}
With this form, we break this sampling step into two. We first sample among $P + 1$ options for the agreement pattern between $B_j$ and its potential link. Define $r$ as an arbitrary set of records. We have
\begin{align}
	\label{eqn:gibbs1}
	p\left( Z_j^{(s+1)} \in r \mid \tilde{\gamma}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}N_{p_j}}{n_A}  w_{p}^{(s+1)},  & r = r_{p_j}; \\
		1- \pi^{(s+1)} , &  r = \{n_A + j\}. \\
	\end{cases}
\end{align}
Since all records in $A$ sharing the same agreement pattern with $B_j$ are equally likely, we then sample among candidate records uniformly using
\begin{align}
	\label{eqn:gibbs2}
	p\left(Z_j^{(s+1)} = q \mid Z_j^{(s+1)} \in r, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)} \right) = \begin{cases} 
		\frac{1}{N_{p_j}}, & r = r_{p_j} \text{ and } q \in r; \\
		1, & r = \{n_A + j\} \text{ and} \\
		& q = n_A + j. \\
	\end{cases}
\end{align} 
Note that sampling from (\ref{eqn:gibbs1}) has complexity $O(P+1)$ and sampling (uniformly) from (\ref{eqn:gibbs2}) has complexity $O(1)$, regardless of the size of $r_{p_j}$. In contrast, sampling $Z_j$ from the full conditional provided in (\ref{eqn:z_full_conditional}) has complexity $O(n_A)$, because sampling a value from $n_A$ options with unequal weights requires normalizing the weights to probabilities.

@@

As shown in the full conditionals in (\ref{efficient_alpha}),  (\ref{efficient_beta}), and (\ref{eqn:gibbs1}), all original record pairs are still accounted for through $\mathcal{N}$. We must revise (\ref{eqn:gibbs2}) to account for the reduced number of labels, so instead use
\begin{align}
	\label{eqn:gibbs2-SEI}
	p\left(Z_j^{(s+1)} = q \mid Z_j^{(s+1)} \in r, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)} \right) = \begin{cases} 
		\frac{1}{|r|}, & r = \text{SEI}(r_{p_j}) \text{ and} \\
		& q \in r; \\
		1, & r = \{n_A + j\} \text{ and} \\
		& q = n_A + j \\
	\end{cases}
\end{align}
in the second step of the split sampler. In this way, we can conduct all posterior inference with the memory reduced SEI$(\tilde{\gamma}) = \{\mathcal{P}, \text{SEI}(\mathcal{R}), \mathcal{N}\}$. We provide guidance on choice of $S$ through a simulation in Section~\ref{SEI-sensitivity}.

@@

	In our first simulation, we generate comparison vectors from pre-specified distributions so that we can easily increase the size of the linkage problem. We use $F = 5$ binary comparisons with probabilities for matching and nonmatching pairs shown in Table \ref{Tab:distributions}. For each record in $B$, we simulate $n_A$ comparison vectors, resulting in a comparison matrix $\gamma \in \mathbb{R}^{n_A n_B \times F}$. For $n_B/2$ of these records, there is no match in $A$, so we simulate $n_A$ comparison vectors from the $\bm{u}$ probabilities. For the other $n_B/2$ of these records, there is one match in $A$, so we simulate $1$ comparison vector from the $\bm{m}$ probabilities, and $n_A - 1$ comparison vectors from the $\bm{u}$ probabilities. We compare the run-time of \texttt{fabl} (with no SEI) against \texttt{BRL} as we increase $n_A$ and $n_B$. Since we have five binary comparison fields with no missingness, the number of unique patterns $P$ is bounded above by $2^5 = 32$, a bound which is consistently attained in simulations with more records.

>>>>

In this article, we propose fast beta linkage (\texttt{fabl}), which extends the \texttt{BRL} model for increased efficiency and scalability. We use independent prior distributions for the matching statuses of each record, and modify the decision theoretic technique of \cite{sadinle_bayesian_2017} to ensure our linkage estimates are bipartite. This approach allows us to (1) employ hashing techniques that speed up calculations and reduce computational costs, (2) compute the pairwise record comparisons over large data files via parallel computing, and (3) reduce memory costs through what we call storage efficient indexing. These contributions can allow \texttt{fabl} to perform record linkage on much larger data files than previous Bayesian Fellegi-Sunter models at significantly increased speed with similar levels of accuracy. In particular, computation time under \texttt{BRL} grows quadratically, with the size of each data file, while computation time under \texttt{fabl} grows linearly, only with the size of the smaller data file.

@@

In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data and do all computation simply using the observed data.

@@

%$\{j: I(Z_j \leq n_A); j = 1, \dots, n_B\}$

@@

Similarly, the posterior updates for $\bm{Z}$ depend on the data only through quantities calculated through $\mathcal{N}, \mathcal{P}$, and $\mathcal{R}$. For each pattern $p$, let $w_p =m_p/u_p$.  The contribution to the likelihood in the full conditional for $Z_j$ can be expressed as
\begin{align}
	\mathcal{L}(Z_j\mid  \tilde{\gamma}, \bm{m}, \bm{u}, \pi) = \prod_{p=1}^P u_p^{N_{p_j}} \prod_{i \in r_{p_j}} w_p^{I(Z_j = i)}. \label{likelihood_efficient_z}
\end{align}
Using (\ref{likelihood_efficient_z}), we break this sampling step into two. We first sample among $P + 1$ options for the agreement pattern between $B_j$ and its potential link. Define $r$ as an arbitrary set of records. We have
\begin{align}
	\label{eqn:gibbs1}
	p\left( Z_j^{(s+1)} \in r \mid \tilde{\gamma}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}N_{p_j}}{n_A}  w_{p}^{(s+1)},  & r = r_{p_j}; \\
		1- \pi^{(s+1)} , &  r = \{n_A + j\}. \\
	\end{cases}
\end{align}
Since all records in $A$ sharing the same agreement pattern with $B_j$ are equally likely, we then sample among candidate records uniformly using
\begin{align}
	\label{eqn:gibbs2}
	p\left(Z_j^{(s+1)} = q \mid Z_j^{(s+1)} \in r, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)} \right) = \begin{cases} 
		\frac{1}{N_{p_j}}, & r = r_{p_j} \text{ and } q \in r; \\
		1, & r = \{n_A + j\} \text{ and} \\
		& q = n_A + j. \\
	\end{cases}
\end{align} 
Note that sampling from (\ref{eqn:gibbs1}) has complexity $O(P+1)$ and sampling (uniformly) from (\ref{eqn:gibbs2}) has complexity $O(1)$, regardless of the size of $r_{p_j}$. In contrast, sampling $Z_j$ from the full conditional provided in (\ref{eqn:z_full_conditional}) has complexity $O(n_A)$, because sampling a value from $n_A$ options with unequal weights requires normalizing the weights to probabilities.

@@

As shown in the full conditionals in (\ref{efficient_alpha}),  (\ref{efficient_beta}), and (\ref{eqn:gibbs1}), all original record pairs are still accounted for through $\mathcal{N}$. We must revise (\ref{eqn:gibbs2}) to account for the reduced number of labels, so instead we use
\begin{align}
	\label{eqn:gibbs2-SEI}
	p\left(Z_j^{(s+1)} = q \mid Z_j^{(s+1)} \in r, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)} \right) = \begin{cases} 
		\frac{1}{|r|}, & r = \text{SEI}(r_{p_j}) \text{ and} \\
		& q \in r; \\
		1, & r = \{n_A + j\} \text{ and} \\
		& q = n_A + j \\
	\end{cases}
\end{align}
in the second step of the split sampler. In this way, we can conduct all posterior inference with the memory reduced SEI$(\tilde{\gamma}) = \{\mathcal{P}, \text{SEI}(\mathcal{R}), \mathcal{N}\}$. We provide guidance on choice of $S$ through a simulation in Section~\ref{SEI-sensitivity}.

@@

	In our first simulation, we generate comparison vectors from pre-specified distributions so that we can easily increase the size of the linkage problem. We use $F = 5$ binary comparisons with probabilities for matching and nonmatching pairs shown in Table \ref{Tab:distributions}. For each record in $B$, we simulate $n_A$ comparison vectors, resulting in a comparison matrix $\gamma \in \mathbb{R}^{n_A n_B \times F}$. For $n_B/2$ of these records, there is no match in $A$, so we simulate $n_A$ comparison vectors from the $\bm{u}$ probabilities. For the other $n_B/2$ of these records, there is one match in $A$, so we simulate one comparison vector from the $\bm{m}$ probabilities, and $n_A - 1$ comparison vectors from the $\bm{u}$ probabilities. We compare the run-time of \texttt{fabl} (with no SEI) against \texttt{BRL} as we increase $n_A$ and $n_B$. Since we have five binary comparison fields with no missingness, the number of unique patterns $P$ is bounded above by $2^5 = 32$, a bound which is consistently attained in simulations with more records.

### 2024-02-14 ba_resubmit_template_files/supplement4.tex
new stuff

	Since $\pi$ encodes the rate of matching across the two data files, the full conditional $p(\pi|\gamma, \bm{Z}, \bm{m}, \bm{u}, \alpha_{\pi}, \beta_{\pi})$ depends only on the number of links $n_{AB}(\bm{Z}) = \sum_{i=1}^{n_B}I(Z_j \leq n_A)$ encoded by $\bm{Z}$ and hyperparameters. We have the full conditional
	\begin{align}
		p(\pi |\gamma, \bm{Z}, \bm{m}, \bm{u}) &\propto p(\bm{Z}|\pi)p(\pi) \\
		&\propto \pi^{n_{AB}(\bm{Z})} (1-\pi)^{n_B - n_{AB}(\bm{Z})} \pi^{\alpha_{\pi} -1} (1-\pi)^{\beta_{\pi} -1} \\
		&\propto \pi^{n_{AB}(\bm{Z}) + \alpha_{\pi} - 1} (1-\pi)^{n_A - n_{AB}(\bm{Z}) + \beta_{\pi} -1}.
	\end{align}
	Thus, $\pi^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}$ has a $\text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi})$ distribution.

@@

Following the observation of \cite{wortman2019}, when $B_j$ does not link to any record in $A$, the contribution to the likelihood is simply a product of $u$ parameters, which we will call $c_j$:
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi, Z_j = n_A + j) = \prod_{i=1}^{n_A}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} = c_j.
\end{align}
When $Z_j = q$ for some $q\leq n_A$, we have
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi,  Z_j = q) =\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(\gamma_{qj}^f = l)I_{obs}(\gamma_{qj}^f)}  \prod_{i \neq q}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.
\end{align}
We multiply and divide by the $u$ parameters for the matching record pair to obtain
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi, Z_j = q) &= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(\frac{m_{fl}}{u_{fl}}\right)^{I(\gamma_{qj}^f = l)I_{obs}(\gamma_{qj}^f)}  \prod_{i = 1}^{n_A}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} \\
	&= w_{qj}  c_j.
\end{align}
We can divide the result of each case by $c_j$ to get
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi, Z_j) \propto \begin{cases} 
		w_{qj}, & q \leq n_A; \\
		1, &  q  = n_A + j.
	\end{cases}
\end{align}
Lastly, we multiply the likelihood by the fast beta prior in (\ref{eqn:fast_beta_prior}) to obtain the full conditional
\begin{align}
	\label{eqn:z_full_conditional2}
	p\left(Z_j^{(s+1)}  = q|\gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}}{n_A} w_{qj}^{(s+1)},  & q \leq n_A; \\
		1 - \pi^{(s+1)}, & q  = n_A + j.
	\end{cases}
\end{align}

>>>>

	Since $\pi$ encodes the rate of matching across the two data files, the full conditional $p(\pi|\gamma, \bm{Z}, \bm{m}, \bm{u}, \alpha_{\pi}, \beta_{\pi})$ depends only on the number of links $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B}I(Z_j \leq n_A)$ encoded by $\bm{Z}$ and hyperparameters. We have the full conditional
	\begin{align}
		p(\pi |\gamma, \bm{Z}, \bm{m}, \bm{u}) &\propto p(\bm{Z}|\pi)p(\pi) \\
		&\propto \pi^{n_{AB}(\bm{Z})} (1-\pi)^{n_B - n_{AB}(\bm{Z})} \pi^{\alpha_{\pi} -1} (1-\pi)^{\beta_{\pi} -1} \\
		&\propto \pi^{n_{AB}(\bm{Z}) + \alpha_{\pi} - 1} (1-\pi)^{n_A - n_{AB}(\bm{Z}) + \beta_{\pi} -1}.
	\end{align}
	Thus, $\pi^{(s+1)}|\gamma, \bm{Z}^{(s)}, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}$ has a $\text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi})$ distribution.

@@

Following the observation of \cite{wortman2019}, when $B_j$ does not link to any record in $A$, the contribution to the likelihood is simply a product of $u$ parameters, which we will call $c_j$:
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi, Z_j = n_A + j) = \prod_{i=1}^{n_A}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} = c_j.
\end{align}
When $Z_j = q$ for some $q\leq n_A$, we have
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi,  Z_j = q) =\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(\gamma_{qj}^f = l)I_{obs}(\gamma_{qj}^f)}  \prod_{i \neq q}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.
\end{align}
We multiply and divide by the $u$ parameters for the matching record pair to obtain
\begin{align}
	p(\Gamma_{.j}| \bm{m}, \bm{u}, \pi, Z_j = q) &= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(\frac{m_{fl}}{u_{fl}}\right)^{I(\gamma_{qj}^f = l)I_{obs}(\gamma_{qj}^f)}  \prod_{i = 1}^{n_A}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} \\
	&= w_{qj}  c_j.
\end{align}
Lastly, we multiply the likelihood by the fast beta prior in (\ref{eqn:fast_beta_prior}) in the main text, and divide by $c_j$ to obtain the full conditional
\begin{align}
	\label{eqn:z_full_conditional2}
	p\left(Z_j^{(s+1)}  = q|\gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}}{n_A} w_{qj}^{(s+1)},  & q \leq n_A; \\
		1 - \pi^{(s+1)}, & q  = n_A + j.
	\end{cases}
\end{align}

%Following the observation of \cite{wortman2019}, when $B_j$ does not link to any record in $A$, the contribution to the likelihood is simply a product of $u$ parameters, which we will call $c_j$:
%	\begin{align}
%		\mathcal{L}(Z_j = n_A + j| \bm{m}, \bm{u}, \pi, \Gamma_{.j}) = \prod_{i=1}^{n_A}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} = c_j.
%	\end{align}
%	When $Z_j = q$ for some $q\leq n_A$, we have
%	\begin{align}
%		\mathcal{L}(Z_j = q| \bm{m}, \bm{u}, \pi, \Gamma_{.j}) =\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(\gamma_{qj}^f = l)I_{obs}(\gamma_{qj}^f)}  \prod_{i \neq q}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.
%	\end{align}
%	We multiply and divide by the $u$ parameters for the matching record pair to obtain
%	\begin{align}
%		\mathcal{L}(Z_j = q| \bm{m}, \bm{u}, \pi, \Gamma_{.j}) &= \prod_{f=1}^{F}\prod_{l=1}^{L_f} \left(\frac{m_{fl}}{u_{fl}}\right)^{I(\gamma_{qj}^f = l)I_{obs}(\gamma_{qj}^f)}  \prod_{i = 1}^{n_A}\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} \\
%		&= w_{qj}  c_j.
%	\end{align}
%	We can divide the result of each case by $c_j$ to get
%	\begin{align}
%		\mathcal{L}(Z_j | \bm{m}, \bm{u}, \pi, \Gamma_{.j}) \propto \begin{cases} 
%			w_{qj}, & q \leq n_A; \\
%			1, &  q  = n_A + j.
%		\end{cases}
%	\end{align}
%	Lastly, we multiply the likelihood by the fast beta prior in (\ref{eqn:fast_beta_prior}) and divide by $c_j$ to obtain the full conditional
%	\begin{align}
%		\label{eqn:z_full_conditional2}
%		p\left(Z_j^{(s+1)}  = q|\gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \pi^{(s+1)}\right) \propto
%		\begin{cases} 
%			\frac{\pi^{(s+1)}}{n_A} w_{qj}^{(s+1)},  & q \leq n_A; \\
%			1 - \pi^{(s+1)}, & q  = n_A + j.
%		\end{cases}
%	\end{align}
